---
title: "GibbsMonteCarloSampling"
author: "Ali Rizvi"
date: "11 February 2019"
output: html_document
---


# Sampling 

## Gibbs Monte-Carlo 

First lets store the probability tables in R. 

```{r}
#create C
C = matrix(c(.5,.5), nrow=1, ncol=2) 
dimnames(C) = list(c(),c('cf', 'ct'))

#create CR
CR = matrix(c(.8,.2,.2,.8), nrow=2, ncol=2) 
dimnames(CR) = list(c('cf','ct'), c('rf', 'rt'))

#create CS
CS = matrix(c(.5,.9,.5,.1), nrow=2, ncol=2) 
dimnames(CS) = list(c('cf','ct'), c('sf', 'st'))

#create SRP
SRW = matrix(c(1,.1,.1,.01,0,.9,.9,.99), nrow=4, ncol=2) 
dimnames(SRW) = list(c('srff','srtf', 'srft', 'srtt'), c('wf', 'wt'))
```

Now lets create function to calculate the probability of obtaining a false for each value given the values of the variables that it depends on or that depend on it. 

For this section we will consider, 0 as false, 1 as true.


```{r}
# function for c given s and r
fc <- function(r,s) {
    c0 <- 0.5*CS[1,s+1]*CR[1,r+1]
    c1 <- 0.5*CS[2,s+1]*CR[2,r+1]
    p0 <- c0/(c0+c1)
    
    #return probability of false
    return (p0)
}

#function for s given c, r and w
fs <- function(c,r,w) {
    s0 <- CS[c+1,1] * SRW[(r*2+1)+0,w+1]
    s1 <- CS[c+1,2] * SRW[(r*2+1)+1,w+1]
    p0 <- s0/(s0+s1)
    
    #return probability of false
    return (p0)
}

# function for r given c, s and w
fr <- function(c,s,w) {
    r0 <- CR[c+1,1] * SRW[s+1,w+1]
    r1 <- CR[c+1,2] * SRW[s+3,w+1]
    p0 <- r0/(r0+r1)
    
    #return probability of false
    return (p0)
}

# function for w given s and r
fw <- function(r,s) {
    w0 <- SRW[ (r*2+1)+s, 1]
    w1 <- SRW[ (r*2+1)+s, 2]
    p0 <- w0/(w0+w1)
    
    #return probability of false
    return (p0)
}
```

Once we have the functions we can use them to sample our data. So lets first get 1000 samples.

```{r}
# setting seed
set.seed(42)

#create data frame for samples
df <- data.frame(c=double(),r=double(),s=double(),w=double())

#initialized first sample
t <- round(runif(4,0,1))
names(t) <- c('c','r', 's', 'w')


#Creating samples
for (i in 1:1000) {
    
    #create a new sample
    t['c'] <- ifelse(runif(1)>fc(t['r'], t['s']), 1, 0)
    t['r'] <- ifelse(runif(1)>fr(t['c'], t['s'], t['w']), 1, 0)
    t['s'] <- ifelse(runif(1)>fs(t['c'], t['r'], t['w']), 1, 0)
    t['w'] <- ifelse(runif(1)>fw(t['r'], t['s']), 1, 0)
    
    #add new sample to df
    df[nrow(df)+1,] <- t
    
}
```

Lets remove the first hundred of these samples. and extract the joint probabilites of wetgrass adn cloudy and sprinker and rain. 

```{r}
#removing first 100 samples
samples <- df[100:nrow(df),]

#filtering samples for join probabilities
wc <- samples[,c('w', 'c')]
sr <- samples[,c('s', 'r')]
```

Now, lets view the joint probabilities. 

#### Joint probability of Wetgrass with cloudy.

```{r}
#joint probability of wc
table(wc) / nrow(wc)
```

#### Joint probability of Sprinker with Rain.

```{r}
#joint probability of sr
table(sr) / nrow(sr)
```