---
title: "RejectionSampling"
author: "Ali Rizvi"
date: "11 February 2019"
output: html_document
---


# Sampling

## Rejection

#### defining pdf function in R

```{r}
#writing pdf in R
f <- function(x) {(1.5*exp(-1.5*x))}
```

Now lets view what the curve looks like. Lets first identify the limit for x; lets check for 5.

```{r}
f(5)
```

The function value at x=5 is quite low so lets just use that as the limit. now lets just view the curve. 

```{r}
#plot pdf
curve(f, 0,5)
```

For rejection sampling we will make use of the uniform distribution. We know for one unif we will use the limit 0 to 5, to identify x. to identify y, we will need to generate a random number from 0 to max of the function at 0. Hence lets view the value of the function at x=0.

```{r}
# checing max value of function
ymax <- f(0)
paste(c('ymax', ymax))
```

Now lets create a function for the sampling using two uniform distributions. 

```{r}
#function to create histgram
f_sample <- function (n) 
{
    sample <- c()
    while (1) {
        x <- runif(1, 0, 5)
        y <- runif(1, 0, 1.5)
        fx <- f(x)
        if (y < fx) {
            sample <- c(sample, x)
        }
        if (length(sample) == n) {
            return (sample)
        }
    }
}
```

Once the function is created lets take out a thousand samples and then plot them with the pdf. 

```{r}
#taking a thousand samples
sample <- f_sample(1000)
fx <- f(seq(0,2,length.out = 1000))

#creating histogram of plot
hist(sample, freq=FALSE, breaks=40)
curve(f, 0,5, add=TRUE, col='blue')
```
