---
title: "CorrelationCovariance"
author: "Ali Rizvi"
date: "11 February 2019"
header-includes:
   - \usepackage{amssymb}
   - \DeclareMathOperator*{\E}{\mathbb{E}}
   - \DeclareMathOperator*{\V}{\mathbb{V}}
output: html_document
---


## Correlations and Covariance

#### Analytical:




We know that both $X$ and $Y$ are independent standard gaussian random variables. Keeping this in mind we can try and compute the covariance and correlation between $U$ and $V$, where:

\[
\begin{array}{rcl}
U &=& X+Y \\
V &=& 2X + 3Y
\end{array}
\]

Using the formulas 

\[
\begin{array}{rcl}
Cov(X,Y) &=& \E[XY] - \E[X]\E[Y] \\
Cov(X_1 + X_2, Y) &=& Cov(X_1,Y) + Cov(X_2,Y) \\
\E[\alpha X] &=& \alpha \E[X] \\
\E[XY] &=& \E[X]\E[Y]
\end{array}
\]

we obtain the following:

\[
\begin{array}{rcl}
Cov(X-Y, 2X+Y) &=& Cov(X,2X) + Cov(X,3Y) - Cov(Y,2X) - Cov(Y, 3Y)\\
&=& (\E[X2X] - \E[X]\E[2X]) + (\E[X3Y] - \E[X]\E[3Y]) - (\E[X2X] \\
&& - \E[Y]\E[2X]) - (\E[Y3Y] - \E[Y]\E[3Y])\\
&=& [2\E[X^2] - 2\E[X]^2] + [3\E[X]\E[Y] -3\E[X]\E[Y]] - [2\E[Y]\E[X] \\
&& - 2\E[Y]\E[X]] - [3\E[Y^2] - 3\E[Y]^2] \\ 
&=& 2\V[X] + 0 + 0 - 3\V[Y] \\
&=& 2\V[X] - 3\V[Y]\\
&=& 2 - 3 \\
&=& -1
\end{array}
\]

Now to obtain the $Corr(U,Y)$ we make use the following formulas:

\[
\begin{array}{rcl}
Corr(X,Y) &=& \dfrac{Cov(X,Y)}{\sigma_x \sigma_y} \\
\V[X+Y] &=& \V[X] + \V[Y] + 2Cov(X,Y) \text{ ; $Cov(X,Y)=0$ if X and Y are independent RVs} \\
\V[X-Y] &=& \V[X] + \V[Y] - 2Cov(X,Y) \text{ ; $Cov(X,Y)=0$ if X and Y are independent RVs} \\
\V[\alpha X] &=& \alpha^2 \V[X]
\end{array}
\]

Then we can calculate the following:

\[
\begin{array}{rcl}
\V[U] &=& \V[X-Y] \\
&=& \V[X] + \V[Y] \\
&=& 1 + 1\\
&=& 2\\
&&\\
\V[V] &=& \V[2X+3Y] \\
&=& \V[2X] + \V[3Y] \\
&=& 2^2\V[X] + 3^2\V[Y] \\
&=& 4 + 9 \\
&=& 13 \\
&&\\
Corr(U,V) &=& \dfrac{Cov(U,V)}{\sqrt{\V[U]\V[V]}}\\
&=& \dfrac{-1}{\sqrt{2\cdot13}}\\
&=& -0.196
\end{array}
\]

#### Simulation:

```{r}

#generating random variables from gaussian
x = rnorm(1000000,0,1)
y = rnorm(1000000,0,1)
u = x - y
v = 2*x + 3*y

#storing values 
U <- data.frame(U=u)
V <- data.frame(V=v)
X <- data.frame(X=x)
Y <- data.frame(Y=y)

#calculating the variance and covariance of the Random Variables
var_x <- var(X)
var_y <- var(Y)
cov_uv <- cov(U,V)
cor_uv <- cor(U,V)

```

Output:

```{r}

cov_uv # The covariance of RVs U and V.
cor_uv # The correlation of RVs U and V.

```

<br>
